How wise is the crowd: Can we infer people are accurate and competent merely because they agree with each other?

### 2024-11-24 README.qmd
update README

*Estimated run time*: Rendering the `anonymized.Rmd` document takes about 2mins on our machine (see [session info](#session-info))

@@

- `appendix*` files contain the appendices that are automatically added `paper.Rmd` when rendering the file.
- `Cogsci*` files are documents used to generate the initial submission of a shorter version of our paper for the CogSci 2024 conference.
- `Experiment*` folders contain all files related to the respective experiment. The `/data` folders contain the raw data (`qualtrics.csv`) and cleaned data (`cleaned.csv`). The cleaning can be reproduced by running the `cleaning.Rmd`. `Experiment_1` and `Experiment_4` also contain the code for the simulations (`model.Rmd`) and several data files with simulated data. 
- `functions/` folder contains functions that we rely upon in our analysis scripts. To keep the `paper.Rmd` document neat and readable, we wrote all lengthy code bits as external functions.
- figures includes images used in the `paper.Rmd` file
- `howwise_0131_initial_submission.pdf` is the initial, and `howwise_0131.pdf` the final submission (after review) to the CogSci 2024 conference, based on the raw files but edited in [overleaf](https://www.overleaf.com/). 
- `output` folder lists all figures generated by the `paper.Rmd` file as `.png` and `.pdf` files.
- `paper.pdf` is the rendered version of `paper.Rmd`
- `references.bib` contains the references
- `stimuli` folder contains all stimuli

>>>>

*Estimated run time*: Rendering the `paper.Rmd` document takes about 2mins on our machine (see [session info](#session-info))

@@

- `appendix*` files contain the appendices that are automatically added `paper.Rmd` when rendering the file.
- `Cogsci*` files are documents used to generate the initial submission of a shorter version of our paper for the CogSci 2024 conference.
- `Experiment*` folders contain all files related to the respective experiment. The `/data` folders contain the raw data (`qualtrics.csv`) and cleaned data (`cleaned.csv`). The cleaning can be reproduced by running the `cleaning.Rmd` files. `Experiment_1` and `Experiment_4` also contain the code for the simulations (`model.Rmd`) and several data files with simulated data. 
- `functions/` folder contains functions that we rely upon in our analysis scripts. To keep the `paper.Rmd` document neat and readable, we wrote all lengthy code bits as external functions.
- figures are generated in the code of the `paper.Rmd` file
- `howwise_0131_initial_submission.pdf` is the initial, and `howwise_0131.pdf` the final submission (after review) to the CogSci 2024 conference, based on the raw files but edited in [overleaf](https://www.overleaf.com/). 
- running the `paper.Rmd` file will generate an `output` folder which lists all figures generated by the `paper.Rmd` file as `.png` and `.pdf` files.
- `paper.pdf` is the rendered version of `paper.Rmd`
- `references.bib` contains the references
- `stimuli` folder contains all stimuli
